\documentclass[11pt]{article}

\usepackage{setspace}
\usepackage[activate={true,nocompatibility},
            final,
            tracking=true,
            kerning=true,
            spacing=true,
            factor=1100,
            stretch=10,
            shrink=10]{microtype}
\usepackage{lipsum}

\microtypecontext{spacing=nonfrench}

\doublespacing

\setlength\parskip{1ex}
\setlength\parindent{1em}

\begin{document}

{\Huge FILE INDEX}\\*
Casey Burklow, Isaac Dudney, KC Guzman, Matthew Hinze

FORMAT:

\texttt{/location/} Filetype\\*
\texttt{file.extension} - description
\vspace{4em}

\texttt{/} PHP files\\*
\texttt{additem.php} - The PHP function to add a new product listing (item) to the database. Uses a form to accept the needed data.\\*
\texttt{admin.php} - Admin management page. Written in PHP, sending SQL commands with escalated priviledge.\\*
\texttt{bid.php} - Server-side logic for updating bid information on an item. No userfacing code is in this script.\\*
\texttt{dash-2.php} - Profile page. Doubles as user preferences page if logged in. Has a list of items that user has created, and preferences if the user is logged in.\\*
\texttt{dash.php} - Fallback for the previous; less featured but known-stable so we keep it just in case. UNUSED.\\*
\texttt{deleteitem.php} - Serverside script for deleting an item, requires the user to be the original poster or an admin to be deleted.\\*
\texttt{deleteuser.php} - Serverside script for deleting a user, requires the user to be an admin to be deleted.\\*
\texttt{edititem.php} - Item edit page for the user that submitted it, in case they want to change the tags/description/title of the work. This is purely the user-facing side of the function, no backend stuff happens here.\\*
\texttt{index.php} - Main page. Includes the slideshow for the featured items.\\*
\texttt{logout.php} - Literally just a link to log the user out.\\*
\texttt{moditem.php} - Serverside script for editing item, edititem.php calls this function to execute the actual edit (no logic stored in edititem.php, it's just userfacing code).\\*
\texttt{newitem.php} - Form to add a new item to the database.\\*
\texttt{product.php} - Main page for an item, this is what happens if you click on a title in a search.\\*
\texttt{search.php} - Logic for search form in the header. Searches through database for text entered into form.\\*
\texttt{updateuser.php} - Logic for updating user information, includes server-side logic and submits to itself.

\texttt{/} CSS files\\*
\texttt{index.css} - primary CSS for the main body of every page; most of the pages share CSS elements, so it's more efficient to reference just one for the body. There is a separate one for the header.

\texttt{/classes/} PHP files\\*
\texttt{password.php} - Hashes the password for storage on the server; since it's a big security risk to store plaintext passwords, we hash the passwords and store the hashes in the server's database.\\*
\texttt{user.php} - enters user data into server's database, including password hash.

\texttt{/includes/} PHP files\\*
\texttt{config.php} - Configuration for the server. Includes PDO connection, timezone, email address, database IP address, and more.

\texttt{/layout/} PHP files\\*
\texttt{footer.php} - Global footer file. Inserted at the end of the index page, unneeded on other webpages.\\*
\texttt{header.php} - Global header file. Includes login form, search form, hero banner, logo, categories drop down.

\texttt{/layout/} CSS files\\*
\texttt{index.css} - Header/footer CSS file. Includes media queries to ensure RWD for the entire header down to original iPhone width screens.

\end{document}
